Generating Simulated Data

### 2021-03-30 docs/SimData.Rmd
almost writing growth pars csv

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))
  #plot len-age data and start values, some are bad
  svlenage_pl <- svlenage %>%
    group_by(species, era) %>%
    group_map(~vbStarts(length~avgage,data=cur_group(),plot=TRUE))

# rearrange into length bins and write length comp data csvs
#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

@@

>>>>

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))

  # try different start points to see if we can get more species fit
  # this one goes to 11!
  # need because group_map doesn't keep group names
  gk <- svlenage %>%
    group_by(species, era) %>%
    group_keys()

  svvbgf3.2 <- svlenage %>%   
    dplyr::group_by(species, era) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                       start = vbStarts(length~avgage,data = .,methLinf="longFish"))))

  #this gets exponential growth pars, probably won't use this growth mod though
  svexp3 <- svlenage %>%
    dplyr::group_by(species, era) %>%
    group_modify(~ broom::tidy(lm(log(length) ~ log(avgage), data = .x))) %>%
    select(species, era, term, estimate) %>%
    pivot_wider(names_from = "term", values_from = "estimate") %>%
    mutate(psi = exp(`(Intercept)`)) %>%
    rename(kappa = `log(avgage)`) %>%
    select(species, era, kappa, psi)

  vbout.2 <- data.frame() 
  for(i in 1:length(svvbgf3.2)) {
    if(is.list(svvbgf3.2[[i]])) {
      spe <- cbind(as.data.frame(gk)[i,], as.data.frame(t(coef(svvbgf3.2[[i]]))))
      vbout.2 <- rbind(vbout.2, spe)
    }
  }

  growthpars <- left_join(svexp3, vbout.2)

  maxera <- growthpars %>% 
    filter(!is.na(Linf)) %>% 
    group_by(era) %>% 
    tally() %>%
    filter(n==11) %>%
    select(era)

  growthspp <- growthpars %>%
    filter(era==maxera) %>%
    select(species, psi, kappa, Linf, K) %>%
    t() %>%
    as.data.frame()

  write_csv(paste0(o.name,"growth_species_NOBA_",s,".csv"))
}
```

Arrange lengths into appropriate bins:

```{r lendat}
# rearrange into length bins and write length comp data csvs
#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

@@

#plot len-age data and start values, some are bad
  svlenage_pl <- svlenage %>%
    group_by(species, era) %>%
    group_map(~vbStarts(length~avgage,data=cur_group(),plot=TRUE))
